---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# monashtipr

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/jimmyday12/monash_tipr/branch/master/graph/badge.svg)](https://codecov.io/gh/jimmyday12/monash_tipr?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of monashtipr is to provide an API to the Monash AFL Tipping competition.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` {r, echo = TRUE, results = 'hide'}
# install.packages("devtools")
devtools::install_github("jimmyday12/monash_tipr")
```
## Workflow

The main workflow is to grab the games for the upcoming round, edit the tips related to the competition and then submit them. 

First we pull down the games. I've chosen to store my password and username in an Renviron file here to keep them secret, but you could pass these in via plain text. Read up on options for this [here](https://cran.r-project.org/web/packages/httr/vignettes/secrets.html)

```{r store_password}
library(monashtipr)

# Store password and username
# If wanted - store user/password in Renviron file
# e.g. you can run `usethis::edit_r_environ()` and edit them
# MONASH_USER = xxx
# MONASH_PASS = xxx

user <- Sys.getenv("MONASH_USER")
pass =  Sys.getenv("MONASH_PASS")

```

Now we can pull games. 
```{r get_games}
comp = "normal"
round = 8
games <- get_current_games(user, pass, comp = comp, round = round)

games
```

Next - we edit the games data frame to add our tips. How you do this will vary by how you actually store your tips - you might do a join with your existing model output for example. I'll leave that up to the user. A simple example would be to provide a vector of margins. 

Please note - these should always be the margin tip of the HOME TEAM.

```{r add_tips}
games$Margin <- c(1, 6, 4, 4, 20, -1, -2, -12, -7)
games
```

Now we just pass this back with our original credentials and we are good to go! =

```{r submit_tips, eval=FALSE, include=TRUE}
submit_tips(games, user, pass, round = round, comp = comp)
```

